Paper figures

### 2020-03-22 voltagebudget/analysis/paper_figures_lossy.Rmd
- Added Fig 10 - Reorg shared data import for VB plots

# HERE - need to run sims to make the osc_times df
p3 <- osc_times %>% 
  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  facet_grid(.~As) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  ggtitle("Compression\nby oscillation")

# Figure 9 - trade-off (with osc)
```{r, message=FALSE}
# --------------------------------------------------------------------
vb_results <- NULL

@@

# Ratio ests
vb_mean_results_ratios <- NULL
freqs <- unique(vb_mean_results$freq)
for (f in freqs) {
  tmp <- filter(vb_mean_results, f == freq, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, f)
  vb_mean_results_ratios <- rbind(vb_mean_results_ratios, row)
}
vb_mean_results_ratios <- as.data.frame(vb_mean_results_ratios, stringsAsFactors=FALSE)
colnames(vb_mean_results_ratios) <- c("error_50", "ratio", "freq")
```
```{r, message=FALSE, fig.width=3.8, fig.height=1.8}

vb_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(x=As, y=variances_pop*ms, color=As*1e9)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Peak amplitude (namps)", y="Compression (ms)") +
  lims(y=c(7,9)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  theme_classic() + 
  theme(legend.position="none") -> p1

vb_norm_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(x=As, y=errors_pop*ms, group=N, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Peak amplitude (namps)", y="Error (ms)") +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  theme_classic() +
  theme(legend.position="none") -> p2

vb_norm_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(y=variances_pop*ms, x=errors_pop*ms, group=N, color=As)) +
  geom_point(alpha=0.8, size=1) +
  labs(x="Error (ms)", y="Compression (ms)") +
  lims(y=c(7,9)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  ggtitle("Compression/error trade-off\nfor oscillation") +
  theme_classic() -> p3

@@

>>>>

# Load shared VB data
```{r, message=FALSE}
# --------------------------------------------------------------------
vb_results <- NULL

@@

# Ratio ests
vb_mean_results_ratios <- NULL
freqs <- unique(vb_mean_results$freq)
for (f in freqs) {
  tmp <- filter(vb_mean_results, f == freq, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, f)
  vb_mean_results_ratios <- rbind(vb_mean_results_ratios, row)
}
vb_mean_results_ratios <- as.data.frame(vb_mean_results_ratios, stringsAsFactors=FALSE)
colnames(vb_mean_results_ratios) <- c("error_50", "ratio", "freq")
```

# HERE - need to run sims to make the osc_times df
osc_times <- NULL
p3 <- osc_times %>% 
  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  facet_grid(.~As) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  ggtitle("Compression\nby oscillation")

# Figure 9 - trade-off (with osc)
```{r, message=FALSE, fig.width=3.8, fig.height=1.8}
vb_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(x=As, y=variances_pop*ms, color=As*1e9)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Peak amplitude (namps)", y="Compression (ms)") +
  lims(y=c(7,9)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  theme_classic() + 
  theme(legend.position="none") -> p1

vb_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(x=As, y=errors_pop*ms, group=N, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Peak amplitude (namps)", y="Error (ms)") +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  theme_classic() +
  theme(legend.position="none") -> p2

vb_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(y=variances_pop*ms, x=errors_pop*ms, group=N, color=As)) +
  geom_point(alpha=0.8, size=1) +
  labs(x="Error (ms)", y="Compression (ms)") +
  lims(y=c(7,9)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  ggtitle("Compression/error trade-off\nfor oscillation") +
  theme_classic() -> p3

@@

# Figure 10 - E50 intro
```{r, message=FALSE, fig.width=3, fig.height=2.8}
# Norm and annotate health versus path
vb_mean_results %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) -> vb_norm_results

vb_norm_results$state <- rep("pathological", nrow(vb_norm_results))
m <- vb_norm_results$errors_pop <= 0.5
vb_norm_results$state[m] <- "healthy"

# Create plots
vb_norm_results %>% 
  filter(freq == 8) %>% 
  ggplot(aes(x=As*1e9, normalize(errors_pop))) +
  geom_point(size=0.8, alpha=0.9) +
  labs(x="Peak\namplitude (namps)", y="Normalized\nError") +
  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
  annotate("text", x = 0.1, y = 0.62, label = expression(paste("E"[50]))) +
  theme_classic() -> p1

vb_norm_results %>% 
  filter(freq == 8) %>% 
  ggplot(aes(x=As*1e9, normalize(variances_pop))) +
  geom_point(size=0.8, alpha=0.9) +
  labs(x="Peak\namplitude (namps)", y="Normalized\ncompression") +
  geom_vline(xintercept = 0.032, alpha=1, color="grey", linetype="dashed") +
  annotate("text", x = 0.046, y = 0.93, label = expression(paste("E"[50]))) +
  theme_classic() -> p2

vb_norm_results %>% 
  filter(freq == 8) %>% 
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=1.2, alpha=1) +
  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
  annotate("text", x = 1, y = 0.54, label = expression(paste("E"[50]))) +
  labs(y="Normalized\nError", x="Normalized\ncompression") +
  ggtitle("A prediction for\npathological oscillation") +
  scale_color_manual("State", values=c("palevioletred3", "peachpuff3")) +
  theme_classic() +
  theme(legend.background = element_rect(colour ="black"),
        legend.position = "right") -> p3

(p1 | p2) / p3 +
  plot_layout(heights = c(1, 3)) + 
  plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = 'a', tag_suffix = ".") 
ggsave("figures/lossy_fig10.png", dpi=600)
```
